Scarid Flight Response, Antigua

### 2019-09-18 r/FID.Rmd

# FID by species
```{r}
fid.sum <- fid %>%
  group_by(species, phase) %>%
  summarize(fid_mean = mean(fid_cm/100),
            fid_max = max(fid_cm/100)) %>%
  rename(max = fid_max,
         mean = fid_mean) %>%
  melt() %>%
  rename(fid = value)

ggplot(fid, aes(x = species, y = fid_cm)) +
  geom_boxplot()

ggplot(fid.sum %>% filter(phase == "Initial"), aes(x = species, y = fid, group = variable)) +
  geom_point(aes(color = variable))
```

@@

# bump distance by spear, site
```{r}
bump <- FID %>% filter(Bump.distance.cm != 0)
lmBump <-lm(data=bump,Bump.distance.cm~Spear + Site + Species + Rugosity + Pre.Approach.Activity)
summary(lmBump)
aov()

ggplot(bump, aes(x=Spear,y=Bump.distance.cm)) + geom_point(aes(color=Species))
```

>>>>

# FID by species
```{r}
fid.sum <- fid %>%
  group_by(species) %>%
  summarize(n=n(),
            fid_mean = mean(fid_cm/100),
            fid_mean_se = sd((fid_cm/100))/sqrt(n),
            fid_max = max(fid_cm/100))

fid.ch2sum <- fid.sum %>%
  filter(species %in% c("Queen","Stoplight"))
```

@@

# bump distance by spear, site
```{r}
bump <- fid %>% filter(bump_distance_cm != 0)
lmBump <-lm(data=bump,bump_distance_cm ~ spear + site + species + rugosity + pre_approach_activity)
summary(lmBump)
aov(lmBump)

ggplot(bump, aes(x=spear,y=bump_distance_cm)) + geom_point(aes(color=species))
```
